---
title: "Text Analytics on 10K Forms"
author: "Hazirah Muhammad"
date: "6/23/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(knitr)
library(dplyr)
library(stringr)
library(rbenchmark)
library (udpipe)
library(XML)
library(lubridate)
library(readr)
library(data.table)
library(textclean)

# Download Forms 10-K from SEC
library(edgar)

# For sentiment datasets
library(parallel)
library(sentimentr)
library(quanteda)
library(tidytext)
library(textstem)
library(rvest)
library(ggplot2)
library(tidyr)
library(reshape2)

# part B
library(tidyquant)
library(tm)
library(SentimentAnalysis)
library(BatchGetSymbols)
library(koRpus)
library(quantmod)

# part C
library(koRpus)
library(stm)
library(wordcloud)
```

# 1. Part A: Construction of Corpus – Fetching 10-K forms from EDGAR

## 1.1 Selection of 30 companies

We have chosen to select 30 companies focusing on only certain sub industry to provide better comparison of data across sectors. Out of the 13 categories of sub industry, we have focused on reviewing only six. Our selection was based on the followings.

1) Sub industry with the highest number of companies - it would be more meaningful to analyse data of companies in the same industry.

2) Market capitalisation - to analyse whether stock price in bigger companies with higher market capitalisation is affected by the SEC filings

```{r}
# Read list of 30 companies excel file
company <- read_xlsx("company_new.xlsx")

# Rename Columns
colnames(company) <- c("Symbol", "Security", "GICS_Sector", "GICS_Sub_Industry", "CIK", "Market_Cap")

# Format column types
company$Symbol <- as.character(company$Symbol)
company$Security <- as.character(company$Security)
company$GICS_Sector <- as.character(company$GICS_Sector)
company$GICS_Sub_Industry <- as.character(company$GICS_Sub_Industry)
company$CIK <- as.integer(company$CIK)
company$Market_Cap <- as.integer(company$Market_Cap)

company
```

## 1.2 Inspect the master index

```{r, eval=FALSE}
# Download master index for year 2010 to 2020
edgar::getMasterIndex(2010:2020)
```

```{r eval=FALSE}
# Load all information from Master Index .Rda files into a data frame
master_index <- data.frame()
for (i in 2010:2020){
  file_name <- paste0("Master Indexes/", i, "master.Rda")
  load(file_name)
  index_h <- year.master %>%
    filter(cik %in% c(company$CIK), form.type %in% c("10-K"))
  
  master_index <- rbind(master_index, index_h)
}

```


```{r eval=FALSE}
# Format column type for master Index
master_index$cik <- as.character(master_index$cik) %>% as.integer()
master_index$company.name <- as.character(master_index$company.name)
master_index$form.type <- as.character(master_index$form.type)
master_index$date.filed <- as.Date(master_index$date.filed)
master_index$edgar.link <- as.character(master_index$edgar.link)
master_index <- master_index %>%
  mutate(year = format(as.Date(master_index$date.filed, "%Y, %m, %d"), "%Y"))
master_index$year <- as.integer(master_index$year)

# Rename Columns in Master Index
colnames(master_index) <- c("CIK", "Security", "Form_Type", "Date_Filed", "Edgar_Link", "Quarter", "Year")

master_index
```

```{r eval=FALSE, echo= FALSE}
saveRDS(master_index, "master_index.rds")
```

```{r echo =FALSE}
master_index_10K <- readRDS("master_index.rds")
```


## 1.3 Get Management Discussions & Analysis from Edgar

```{r eval=FALSE}
# Download management discussions
edgar::getMgmtDisc(cik.no = company$CIK, filing.year = c(2010:2020))
```


```{r}
# Combine management discussions in a dataframe
mgmt_disc_df <- data.frame()

file_list <- list.files("MD&A section Text")
file_path <- paste0("MD&A section Text/", file_list)

for (i in 1:length(file_path)) {
  file <- readLines(file_path[i])
  
  mgmt_disc <- tibble(cik = as.integer(gsub("CIK:","",file[1])),
                      company_name = (gsub("Company Name:","", file[2])),
                      date_filed = gsub("Filing Date:","",file[4]),
                      accession_no = gsub("Accession Number:","", file[5]),
                      #remove punctuations, numbers and space
                      mgmt_disc = gsub("as of","", tolower(file[8])) %>%
                        tm::removePunctuation() %>%
                        tm::removeNumbers()%>%
                        tm::stripWhitespace())
  
  mgmt_disc_df <- bind_rows(mgmt_disc_df, mgmt_disc)
}

#Rename columns for Management Discussions Table
colnames(mgmt_disc_df) <- c("CIK", "Company_Name", "Date_Filed", "Accession_Number", "Text")

mgmt_disc_df$CIK <- as.character(mgmt_disc_df$CIK) %>% as.integer()
mgmt_disc_df$Company_Name <- as.character(mgmt_disc_df$Company_Name)
mgmt_disc_df$Date_Filed <- as.Date(mgmt_disc_df$Date_Filed)

# Add in Year columns
mgmt_disc_df <- mgmt_disc_df %>% mutate(Year = format(as.Date(mgmt_disc_df$Date_Filed, "%Y, %m, %d"), "%Y"))
mgmt_disc_df$Year <- as.integer(mgmt_disc_df$Year)

# Add in Quarter columns
mgmt_disc_df <- mgmt_disc_df %>% mutate(Quarter = substr(quarters(as.Date(Date_Filed)), 2, 2))
mgmt_disc_df$Quarter <- as.integer(mgmt_disc_df$Quarter)

# Merge with Master Index Table
merge_mda <- mgmt_disc_df %>% 
  unique() %>% 
  inner_join(company, by=c("CIK"="CIK"))

merge_mda <- merge_mda %>%
  select(CIK, Symbol, Security, Company_Name, GICS_Sub_Industry, Date_Filed, Quarter, Year, Accession_Number, Text)
```


```{r}
saveRDS(merge_mda, "merge_mda.rds")
```

```{r}
merge_mda <- readRDS("merge_mda.rds")
```


## 1.4 Import Stop Words

We have imported Loughran and McDonalds stopwards in the website at https://sraf.nd.edu/textual-analysis/resources/

```{r}
# Stopwords from Loughran and McDonland's
stopw_loughran_mcdonald <- read_excel("loughran_stopwords.xlsx")

#Set columns structure
stopw_loughran_mcdonald$word <- as.character(stopw_loughran_mcdonald$word)

#Lowercase all words in table
stopw_loughran_mcdonald$word <- tolower(stopw_loughran_mcdonald$word)

# Add customised stopwords
stopw_custom <- c("financial", "statement", "exhibit", "report", "figure", "fig", "table", "company", "footnote", "page")

# Finalising stopwords
stopw_final <- rbind(stopw_loughran_mcdonald, stopw_custom)
```

```{r}
library(tidytext)
library(httr)
library(textclean)
library(lexicon)
data("stop_words") # Multilangual stopwords list
data("sw_fry_1000") # Fry's 1000 Most Commonly Used English Words

fry <- as.data.frame(lexicon::sw_fry_1000) %>% rename(word = `lexicon::sw_fry_1000`)

# Create a function to automatically remove digit,
# remove punctuations and transform all letters to lower
stopword_funct <- function(x){
  x <- gsub('[[:digit:]]+',' ', x)
  x <- gsub('[[:punct:]]+',' ', x)
  x <- tolower(x)
  return(x)
} 

# Symbol as stopwords
merge_mda$Symbol <- stopword_funct(merge_mda$Symbol)

Symbol <- merge_mda %>% 
  select(Symbol) %>%
  unique(.)

symbol_stopwords <- merge_mda$Symbol


# Company name as stopwords
merge_mda$Company_Name <- stopword_funct(merge_mda$Company_Name)

company_name <- merge_mda %>% 
  select(Company_Name) %>%
  unnest_tokens(word, Company_Name) %>%
  select(word) %>%
  unique(.)

company_name_stopwords <- company_name$word

# GICS Sub Industry as stopwords
merge_mda$GICS_Sub_Industry <- stopword_funct(merge_mda$GICS_Sub_Industry)

subindustry <- merge_mda %>% 
  select(GICS_Sub_Industry) %>%
  unnest_tokens(word, GICS_Sub_Industry) %>%
  select(word) %>%
  unique(.)

subindustry_stopwords <- subindustry$word

custom_stopwords <- tibble(word = unique(c(company_name_stopwords, subindustry_stopwords, symbol_stopwords)), lexicon = "custom")

# Create custom stop words list
custom_stopwords <- rbind(stop_words, custom_stopwords)
```


## 1.5 Tokenisation
```{r}
# Tokenize and remove stopwords
mda_tokens <- merge_mda %>%
  unnest_tokens(word, Text) %>%
  anti_join(custom_stopwords) %>%
  anti_join(fry) %>%
  anti_join(stopw_final) %>%
  filter(! word %in% sw_fry_100) 

format(length(mda_tokens$Accession_Number), big.mark = ",")

head(mda_tokens, 10)
```

## 1.6 Stemming and Lemmatisation

Download language model and define cores for parallel processing 
```{r eval=FALSE, echo= FALSE}
# Run approximately 20 mins
# Download english model from udpipe
langmodel_download <- udpipe::udpipe_download_model("english")

# Load model
langmodel <- udpipe::udpipe_load_model(langmodel_download$file_model)

# Specify the number of cores
no_cores <- parallel::detectCores() - 1

# Run udpipe on tokenised management discussions
postagged_mda <- udpipe:: udpipe(object = langmodel, x = mda_tokens$word, parallel.cores = no_cores,
                    parallel.chunks = 100,
                    trace = T)

postagged_mda_df <- as.data.frame(postagged_mda)

# Initiate cluster
cl <- parallel::makeCluster(no_cores)

# Stop cluster
parallel::stopCluster(cl)
```
```{r eval=FALSE, echo= FALSE}
saveRDS(postagged_mda_df, "postagged_tokens_mda.rds")
```

```{r}
postagged_mda_df <- readRDS("postagged_tokens_mda.rds")
```


* Joining the lemmatized udpipe output of management discussions with the other variables in the data frame
```{r}
mda_tokens <- mda_tokens %>% 
  mutate(doc_id = row_number())

length(unique(mda_tokens$doc_id))
length(unique(postagged_mda_df$doc_id))

postagged_mda_df_joined <- postagged_mda_df  %>% 
  mutate(doc_id = as.numeric(doc_id)) %>% 
  left_join(mda_tokens)
```

* Removing short and long words from listings output of udpipe
```{r}
postagged_mda_df_joined$word_length <- nchar(postagged_mda_df_joined$lemma)

quantile(postagged_mda_df_joined$word_length, c(0.025, 0.975))

length(postagged_mda_df_joined$lemma)
```



```{r}
#remove all words that are longer than 13 characters and shorter than 3 characters
postagged_mda_df_joined_shortened <- postagged_mda_df_joined %>% filter(between(word_length, 4, 13))
length(postagged_mda_df_joined_shortened$lemma)
length(postagged_mda_df_joined$lemma) - length(postagged_mda_df_joined_shortened$lemma)
```

Out of 734,931 tokenised words, 52,544 words will be removed.

## 1.7 Removing Stopwords again after lemmatisation on Management Discussions & Analysis
```{r}
# Removing stopwords again after lemmatisation
postagged_mda_df_joined_short <- postagged_mda_df_joined_shortened %>% 
  mutate(word = lemma) %>% 
  anti_join(custom_stopwords ) %>%
  anti_join(stopw_final) %>%
  anti_join(fry) %>%
  filter(! word %in% sw_fry_100) 
length(postagged_mda_df_joined_short$lemma)

# Calculate difference
format((length(postagged_mda_df_joined_shortened$lemma) -length(postagged_mda_df_joined_short$lemma)), big.mark = ",")
```

After removing stopwords again, the tokenised words are further reduced by 98,488 words.

```{r}
saveRDS(postagged_mda_df_joined_short, "postagged_mda_df_joined_short")
```

```{r}
clean_mda <- readRDS("postagged_mda_df_joined_short")
```


## 1.8 Performing TF-IDF
```{r calc_word_counts}
# Calculate word counts
tokens_count_all <- clean_mda %>% 
  count(lemma, sort = TRUE)

tokens_count_mda <- clean_mda  %>%
  group_by(Accession_Number) %>% 
  count(lemma, sort = TRUE)
```

```{r tf-idf_calc}
# TF_IDF on management discussions
TF_IDF <- tokens_count_mda %>% 
  bind_tf_idf(lemma, Accession_Number, n) %>% 
  arrange(desc(tf_idf))

TF_IDF
```


```{r}
# Inspect TF-IDF cut-precentile 
tf_idf_cutoffs <- quantile(TF_IDF$tf_idf, na.rm = T, c(0.025, 0.975))
quantile(TF_IDF$tf_idf, na.rm = T, c(0.025, 0.975))
```


* Plotting TF_IDF
```{r}
TF_IDF %>% filter(tf_idf <0.0065) %>% 
  ggplot(., aes(x=tf_idf, fill="blue")) + 
  geom_histogram() +
  labs(title="Distribution of TF-IDF", x="TF-IDF", y="Frequency") +
  scale_y_continuous(labels=scales::comma)+ scale_fill_manual(values = c("blue")) +
  theme(legend.position="none")
```


```{r eval=FALSE}
short_merge_mda <- merge_mda %>%
  select("CIK", "Symbol", "Security", "Company_Name", "GICS_Sub_Industry", "Date_Filed", "Year", "Accession_Number")

#Remove tf_idf more than 0.004
tidy_tf_idf <- TF_IDF %>% 
  filter(tf_idf < 0.004 ) %>% 
  mutate(word = lemma) %>% 
  left_join(short_merge_mda)
```

```{r eval=FALSE}
saveRDS (tidy_tf_idf, "tidy_mda.rds")
```

```{r}
tidy_mda <- readRDS("tidy_mda.rds")
```


## 1.9 Analysis on TF-IDF

```{r}
#Analysis by Year
year_tokens <- clean_mda %>% 
  count(Year, word, sort=TRUE) %>% 
  ungroup() %>%
  bind_tf_idf(word,Year, n)

# Plot important terms by years
year_tokens %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  group_by(Year) %>%
  top_n(15) %>%
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill=Year)) +
  geom_col(show.legend = FALSE) +
  labs (x=NULL, y="tf-idf", title="Important Terms by Year") +
  facet_wrap(~ Year, ncol=3, scales = "free") + 
  coord_flip()
```



```{r}
#Analysis by GCIS Sub Industry
gcis_tokens <- clean_mda %>% 
  count(GICS_Sub_Industry, word, sort=TRUE) %>% 
  ungroup() %>%
  bind_tf_idf(word,GICS_Sub_Industry, n)

# Plot important terms by years
gcis_tokens %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  group_by(GICS_Sub_Industry) %>%
  top_n(15) %>%
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill=GICS_Sub_Industry)) +
  geom_col(show.legend = FALSE) +
  labs (x=NULL, y="tf-idf", title="Important Terms by Sub Industry") +
  facet_wrap(~ GICS_Sub_Industry, ncol=3, scales = "free") + 
  coord_flip()
```
## 1.10 Analysis based on dominant words
```{r}
# Count and visualise the top 10 dominant words by GICS Sub Industry
gcis <- clean_mda %>%
  group_by(GICS_Sub_Industry) %>%
  count(word, GICS_Sub_Industry) %>%
  top_n(10,n) %>% ungroup() %>%
  arrange(desc(n)) %>%
  mutate(word2=fct_reorder(word, n))

ggplot(gcis, aes(x=reorder(word2,n), y=n, fill=GICS_Sub_Industry)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~GICS_Sub_Industry, scales="free") +
  coord_flip() + labs(title="DOMINANT WORDS PER SUB-INDUSTRY", x="Frequency", y="Words")
```
```{r}
# Count and visualise the top 10 dominant words by Year
year <- clean_mda %>%
  group_by(Year) %>%
  count(word, Year) %>%
  top_n(10,n) %>% ungroup() %>%
  arrange(desc(n)) %>%
  mutate(word2=fct_reorder(word, n))

ggplot(year, aes(x=reorder(word2,n), y=n, fill=Year)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~Year, scales="free") +
  coord_flip() + labs(title="DOMINANT WORDS PER YEAR", x="Frequency", y="Words")
```




# 2. Part B: Sentiment association with Financial Indicator

## 2.1 Polarity

```{r}
#detokenize
detokens_all <- tidy_mda %>%
  group_by(Accession_Number) %>%
  summarise(clean_text  = paste(word,collapse = "  "), totalwords = n())  %>% 
  dplyr::select(Accession_Number, clean_text) %>%
  inner_join(merge_mda, by="Accession_Number")
```

```{r eval=FALSE}
#Perform polarity on management discussions
pol_all_mda <- qdap::polarity(detokens_all$clean_text)

#Plot ploarity
plot(pol_all_mda)
```
```{r eval=FALSE}
saveRDS(pol_all_mda, "polarity_mda.rds")
```

```{r}
pol_all_mda <- readRDS("polarity_mda.rds")
```

## 2.2 Calculating sentiment measures and loading to sentiment table

```{r}
#Importing Loughran & McDonald's Sentiment
LM_dict <- read_xlsx("LoughranMcDonald_SentimentWordLists_2018 copy.xlsx")

#Set columns structure
LM_dict$sentiment <- as.character(LM_dict$sentiment)
LM_dict$word <- as.character(LM_dict$word)

#Lowercase all words in table
LM_dict$sentiment <- tolower(LM_dict$sentiment)
LM_dict$word <- tolower(LM_dict$word)
head(LM_dict, 10)
```

```{r}
#Creating dummy dictionaries
dummy_LM <- tibble(Accession_Number = 'dummy', 
                   positive=0, 
                   negative=0, 
                   uncertainty=0, 
                   litigious=0, 
                   strong_modal=0, 
                   weak_modal=0,
                   constraining=0 )

dummy_NRC <- tibble(Accession_Number = 'dummy',
                    positive=0,
                    negative=0,
                    anger=0,
                    fear=0,
                    trust=0,
                    sadness=0,
                    suprise=0,
                    disgust=0,
                    joy=0,
                    anticipation=0 )

dummy_bing <- tibble(Accession_Number = 'dummy', 
                     positive=0, 
                     negative=0 )
```


```{r}
# Unnest_tokens again to get clean text
tokenised <- detokens_all %>%
  unnest_tokens(word, clean_text)
```


```{r eval=FALSE}
# Text complexity
n_words <- tokenised %>%
  group_by(word, Accession_Number) %>%
  count (Accession_Number)

n_complex <- tokenised %>%
  group_by(word, Accession_Number) %>%
  mutate(complexity = nchar(gsub("[^X]", "", gsub("[aeiouy]+", "X", tolower (word))))) %>%
  filter(complexity>=3) %>%
  group_by(Accession_Number) %>%
  count(Accession_Number)

complexity <- tibble(Accession_Number = n_words$Accession_Number,
                     complexity = n_complex$n/n_words$n)

```

```{r eval=FALSE}
saveRDS(complexity, "complexity.rds")
```

```{r}
complexity <- readRDS("complexity.rds")
```


```{r}
# Sentiment Loughran Mcdonald
tokens_LM <- tidy_mda %>%
  inner_join(LM_dict, by=c("word"="word"))

word_count_LM <- tokens_LM %>% 
  group_by(Accession_Number) %>% 
  summarise(LM_total_words=n())

sentiment_LM <- tokens_LM %>%
  group_by(Accession_Number, sentiment) %>%
  summarise(total_sentiment = n()) %>%
  spread(sentiment, total_sentiment, fill=0) %>%
  bind_rows(dummy_LM) %>%
  left_join(word_count_LM) %>%
  mutate(LM_sent = positive-negative,
         LM_positive = positive/LM_total_words,
         LM_negative = negative/LM_total_words,
         LM_litigious = litigious/LM_total_words,
         LM_uncertainty = uncertainty/LM_total_words,
         LM_constraining = constraining/LM_total_words ) %>%
  select(-c(positive, negative, litigious, uncertainty, constraining)) %>%
  filter(Accession_Number !="dummy")

# Sentiment Affin
tokens_afinn <- tokenised %>%
  inner_join(get_sentiments("afinn"))

sentiment_afinn <- tokenised %>%
  inner_join(get_sentiments("afinn")) %>%
  group_by(Accession_Number) %>%
  summarise(affin_sent =sum(value))

# Sentiment Bing
tokens_bing <- tokenised %>%
  inner_join((get_sentiments("bing")))

word_count_bing <- tokens_bing %>%
  group_by(Accession_Number) %>%
  summarise(bing_total_words = n())

sentiment_bing <- tokens_bing %>%
  group_by(Accession_Number, sentiment) %>%
  summarise(total_sentiment=n()) %>%
  spread(sentiment, total_sentiment, fill=0) %>%
  bind_rows(dummy_bing) %>%
  left_join(word_count_bing) %>%
  mutate(bing_sent=positive-negative,
  bing_positive = positive/bing_total_words,
  bing_negative = negative/bing_total_words) %>%
  select(-c(positive, negative)) %>%
  filter(Accession_Number !='dummy')

# Sentiment NRC
tokens_nrc <- tokenised %>% inner_join(get_sentiments("nrc"))

word_count_nrc <- tokens_nrc %>% 
  group_by(Accession_Number) %>% 
  summarise(nrc_total_words =n())

sentiment_nrc <- tokens_nrc %>% 
  group_by(Accession_Number, sentiment) %>%
  summarise(total_sentiment=n()) %>%
  spread(sentiment, total_sentiment, fill=0) %>%
  bind_rows(dummy_NRC) %>%
  left_join(word_count_nrc) %>%
  mutate(nrc_sent=positive-negative,
  NRC_positive = positive/nrc_total_words,
  NRC_negative = negative/nrc_total_words,
  NRC_anger = anger/nrc_total_words,
  NRC_fear = fear/nrc_total_words,
  NRC_trust = trust/nrc_total_words,
  NRC_sadness = sadness/nrc_total_words,
  NRC_surprise = surprise/nrc_total_words,
  NRC_disgust = disgust/nrc_total_words,
  NRC_joy = joy/nrc_total_words,
  NRC_anticipation = anticipation/nrc_total_words) %>%
  select(-c(positive, negative, anger, fear, trust, sadness, suprise, disgust,joy, anticipation)) %>%
  filter(Accession_Number !='dummy')
```

```{r}
# Merging sentiment features
sentiment_df <- sentiment_LM %>%
  left_join(complexity) %>%
  left_join(sentiment_afinn) %>%
  left_join(sentiment_bing) %>%
  left_join(sentiment_nrc)
```





## 2.3 Analysis From Word Perspective

To understand the most common positive and negative words in the mda, we apply these 3 dictionaries above on sentiment analysis.

```{r}
# Plot common positive and negative words using Bing dictionary
tokens_bing %>% ungroup()  %>% 
  count(word, sentiment, sort = TRUE) %>% 
  mutate(word = reorder(word, n)) %>% 
  group_by(sentiment) %>% 
  top_n(25) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free") +
  labs(y = "Contribution to sentiment - Bing Dictionary", x = NULL) +
  coord_flip() +
  ggtitle('Words Contributing to Positive & Negative Sentiment in Management Discussions & Analysis')

```

```{r}
# Plot common positive and negative words using Affin dictionary
afinn_word_counts <-  tokenised %>%
  inner_join(get_sentiments("afinn")) %>% 
  ungroup()  %>% 
  mutate(sentiment = ifelse(value>0,"positive","negative")) %>% 
  count(word, sentiment, sort = TRUE)

afinn_word_counts %>%
  mutate(word = reorder(word, n)) %>% group_by(sentiment) %>% 
  top_n(25) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free") +
  labs(y = "Contribution to sentiment - Affin Dictionary", x = NULL) +
  coord_flip() +
  ggtitle('Words Contributing to Positive & Negative Sentiment in Management Discussions & Analysis')

```

## 2.4 Get Stock Information

```{r}
merge_mda <- readRDS("merge_mda.rds")
```

```{r eval=FALSE}
# Get Average Log Return for each company
merge_mda$Symbol <- as.factor(merge_mda$Symbol)

stockreturn_adj_price <-data.frame()

for (r in 1: nrow(merge_mda)){
  tryCatch({
    mda_report <- merge_mda [r, ]
    
    # Extract stock information
    stock_data <- BatchGetSymbols(tickers = mda_report$Symbol,
                                  first.date = mda_report$Date_Filed -7,
                                  last.date = mda_report$Date_Filed +3,
                                  type.return="log")
    
    # FIler the second day and last day
    stock_data_filtered <- stock_data [[2]] %>%
      filter(ref.date == max(ref.date) | row_number()==2) %>%
      arrange(desc(ref.date))
    
    # Calculate stock price change on log scale
    return_adj_price <- mda_report %>% select(Accession_Number) %>% 
      mutate(return_adj_price=stock_data_filtered$ret.closing.prices[1] - stock_data_filtered$ret.closing.prices[2]) #return difference
    
    price_adj_ratio <- mda_report %>% select(Accession_Number) %>%
      mutate(price_adj_ratio = (stock_data_filtered$price.adjusted[1]/ stock_data_filtered$price.adjusted[2]) - 1) # stock price ratio
    
    accession_number <- mda_report$Accession_Number[1]
  })
  stockreturn_adj_price <- rbind(stockreturn_adj_price, return_adj_price)
}

```

```{r eval=FALSE}
saveRDS(stockreturn_adj_price, "stockreturn_adj_price.rds")
```

```{r}
stockreturn_adj_price <-readRDS("stockreturn_adj_price.rds")
```

```{r}
# Merge stock adjustment price with Master Index
stockreturn_adj_pricev <- merge_mda %>% inner_join(stockreturn_adj_price, by=c("Accession_Number"="Accession_Number"))
stockreturn_adjusted_price <- stockreturn_adj_pricev %>% select(-c(Text))
```

```{r eval=FALSE}
# Get Prie Adjustment Ratio for each company 
stockprice_adj_ratio <-data.frame()

for (r in 1: nrow(merge_mda)){
  tryCatch({
    mda_report <- merge_mda [r, ]
    
    # Extract stock information
    stock_data <- BatchGetSymbols(tickers = mda_report$Symbol,
                                  first.date = mda_report$Date_Filed -7,
                                  last.date = mda_report$Date_Filed +3,
                                  type.return="log")
    
    # Filter the second day and last day
    stock_data_filtered <- stock_data [[2]] %>%
      filter(ref.date == max(ref.date) | row_number()==2) %>%
      arrange(desc(ref.date))
    
    # Calculate stock price change on log scale
    return_adj_price <- mda_report %>% select(Accession_Number) %>% 
      mutate(return_adj_price=stock_data_filtered$ret.closing.prices[1] - stock_data_filtered$ret.closing.prices[2]) #return difference
    
    price_adj_ratio <- mda_report %>% select(Accession_Number) %>%
      mutate(price_adj_ratio = (stock_data_filtered$price.adjusted[1]/ stock_data_filtered$price.adjusted[2]) - 1) # stock price ratio
    
    accession_number <- mda_report$Accession_Number[1]
  })
  stockprice_adj_ratio <- rbind(stockprice_adj_ratio, price_adj_ratio)
}

```

```{r eval=FALSE}
saveRDS(stockprice_adj_ratio, "stockprice_adj_ratio.rds")
```

```{r}
price_adj_ratiov <-readRDS("stockprice_adj_ratio.rds")
```

```{r}
# Merge stock adjustment price ratio with Master Index
price_adj_ratio_merge <- merge_mda %>% inner_join(price_adj_ratiov, by=c("Accession_Number"="Accession_Number"))
price_adj_ratio_merge <- price_adj_ratio_merge %>% select(-c(Text))
```


```{r}
# Plot Average Return
stockreturn_adjusted_price$Year <- as.factor(stockreturn_adjusted_price$Year)
return_avg <- stockreturn_adjusted_price %>%
              group_by(GICS_Sub_Industry, Year) %>%
              summarise(return_adj_price = mean(return_adj_price))

return_avg_plot <- return_avg %>%
  ggplot(aes(x = Year, y = return_adj_price, color = GICS_Sub_Industry)) +
  geom_line(aes(group=GICS_Sub_Industry)) +
  labs(title = "Average Log Return between 2010 and 2020 After SEC Filings", 
       subtitle = "Grouping on GICS Sectors", x="Year Filed", y = "Log Return", legend = "GICS Sector") 

# Plot Average Stock Price Change
price_adj_ratio_merge$Year <- as.factor(price_adj_ratio_merge$Year)

price_avg <- price_adj_ratio_merge %>%
              group_by(GICS_Sub_Industry, Year) %>%
              summarise(price_adj_ratio = mean(price_adj_ratio))

price_adj_plot <- price_avg %>%
  ggplot(aes(x = Year, y = price_adj_ratio, color = GICS_Sub_Industry)) +
  geom_line(aes(group=GICS_Sub_Industry)) +
  labs(title = "Average Stock Price Change between 2010 and 2020 After SEC Filings", 
       subtitle = "Grouping on GICS Sectors", x="Year Filed", y = "% Change in Stock Price", legend = "GICS Sector") 

library(ggpubr)

ggarrange(return_avg_plot, price_adj_plot, ncol = 1, nrow = 2)

```



```{r}
# Combine Return Adjusted Price and Price Adjusted Ratio data
v <- price_adj_ratio_merge %>% 
  select(price_adj_ratio, Accession_Number) %>% 
  left_join(stockreturn_adjusted_price)

# Combine price data with postagged management discussion and analysis table
clean_mda_price <- v %>% 
  select(Accession_Number,price_adj_ratio, return_adj_price) %>%
  inner_join(clean_mda, by=(c("Accession_Number" = "Accession_Number")))

# Joining sentiment features with price
sentiment_data <- sentiment_df %>% left_join(price_adj_ratio_merge)
```

## 2.5 Regression Analysis on How Sentiment Analysis Affects Stock Price Change

```{r}
sentiment_regression <- sentiment_data %>%
  select(-c(Year, CIK, Company_Name, GICS_Sub_Industry, Accession_Number, Symbol, Security, Date_Filed, Quarter))

  str(sentiment_regression)

reg_LM <- lm(price_adj_ratio ~ strong_modal + weak_modal + LM_total_words + LM_sent + LM_positive + LM_negative + LM_litigious + LM_uncertainty + LM_constraining, data=sentiment_regression)

reg_bing <- lm(price_adj_ratio ~ bing_total_words+ bing_sent+ bing_positive+ bing_negative, data=sentiment_regression)

reg_afinn <- lm(price_adj_ratio ~ affin_sent, data=sentiment_regression)

reg_nrc <- lm(price_adj_ratio ~ nrc_total_words + nrc_sent + NRC_positive + NRC_negative + NRC_anger +      
 NRC_fear + NRC_trust + NRC_sadness + NRC_surprise + NRC_disgust + NRC_joy + NRC_anticipation, data=sentiment_regression)

reg_final <- stargazer::stargazer(reg_LM, reg_bing, reg_afinn, reg_nrc, type='text')

```

## 2.6 Model Sentiment by GICS Sub Industry

```{r eval=FALSE}
# Model sentiment for every sub industry
model_output_sub_industry <- data.frame()

sector <- price_adj_ratio_merge %>% select(GICS_Sub_Industry)

for (z in 1:length(sector)) {
  model_data <- sentiment_data %>%
  # filter(GICS_Sub_Industry==sector[z]) %>%
    select(-c(Year, CIK, Company_Name,Symbol, Security, Date_Filed, Quarter))
  
# Modelling
  model <- lm(price_adj_ratio ~., data = model_data)
  
# Prep data for plotting
  local_df <- head(as.data.frame(summary(model)$coefficients) %>%
                     tibble::rownames_to_column() %>%
                     #mutate(absolute_t_value = abs('t value')) %>%
                     #arrange(desc(absolute_t_value)), 10) %>%
                     mutate(rowname = factor(rowname, levels = rowname)) %>%
    mutate(significance = case_when('Pr(>|t|)' <= 0.001 ~ 'significant***', 
                                    'Pr(>|t|)' <= 0.01 ~ 'significant**', 
                                    'Pr(>|t|)' <= 0.05 ~ 'significant*', 
                                    TRUE ~ 'not significant')) %>%
    mutate(GICS_Sub_Industry = sub_industry[z]) %>%
    mutate(r_squared = paste('Multiple R-Squared:', as.character(round(summary(model)$r.squared,3))))
  
  model_output_sub_industry<- rbind(model_output_sub_industry, local_df)
  
}

ggplot(model_output_sub_industry, 
       aes(x = reorder(rowname, absolute_t_value), 
           y = absolute_t_value, fill = significance)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 10 Sentiment Features for Predicting Stock Price Change After 10-K Filings", 
       subtitle = "Grouping on GICS Sub Industry", y= "Absolute t-value", x="Features") + 
  ylim(0,4) + coord_flip() +
  facet_wrap(~GICS_Sub_Industry+r_squared, ncol = 4, scales = "free")

rm(model_output_sub_industry)
```


## 2.7 Additional Analysis on Classification By Emotion

```{r}
# NRC Dictionary
tidy_mda %>% inner_join(get_sentiments("nrc")) %>%
  count(sentiment,CIK) %>%
  pivot_wider(names_from = sentiment,values_from = n) %>%
  replace_na(list(anticipation=0,joy=0,positive=0,surprise=0,trust=0,anger=0,disgust=0,fear=0,negative=0,sadness=0)) %>%                           #replace NA with reasonable 0
  mutate(sentiment_nrc = positive-negative) -> emotions_nrc
emotions_nrc <- emotions_nrc %>%
  left_join(price_adj_ratio_merge)

# Plot distribution of emotions
tidy_mda %>% inner_join(get_sentiments("nrc"),by ="word") %>%
  count(sentiment,CIK) %>% 
  mutate(index = row_number()) %>% 
  filter(!sentiment %in%c("positive", "negative")) %>%
  ggplot(aes(x=reorder(sentiment,n), y=n, color=sentiment)) %>%
  + geom_col() + labs(title="Sentiments Count\n(classification by emotion)",x="Sentiment Categories",y="Frequency")
```





# 3. Part C: Topic Modelling and Latent Dirichlet Allocation (LDA)

## 3.1 Structural Topic Modelling (STM)

### 3.1.1 Processing text data in STM
```{r eval=FALSE}
# Reading and processing text data
mda.df <- as.data.frame(clean_mda_price)

mda.df <- mda.df %>% 
  filter(upos %in% c("VERB", "NOUN", "ADJ")) %>%
  group_by(Accession_Number) %>%
  summarise(documents_pos_tagged=paste(lemma, collapse=" "))

subset_mda <- clean_mda_price %>% 
  select(Accession_Number, Year, price_adj_ratio, return_adj_price)

mda_new <- mda.df %>% 
  left_join(subset_mda) %>% 
  distinct(.)

mda_new <- mda_new %>% 
  na.omit(.)
```
```{r eval=FALSE}
saveRDS(mda_new, "mda_new.rds")
```

```{r}
mda_new <- readRDS("mda_new.rds")
```

```{r eval=FALSE}
#Prepare: Associating Text with Metadata
mda_processed <- stm::textProcessor(mda_new$documents_pos_tagged,
                                   metadata = mda_new,
                                   lowercase = FALSE, #not required since this was done by unnest_tokens before
                                   removestopwords = FALSE, #not required since we removed stopwords already
                                   removenumbers = FALSE, #not required since we removed them already
                                   removepunctuation = FALSE, #not required since we removed them already
                                   ucp = FALSE,
                                   stem = FALSE) #not required since the input data was already stemmed & lemmatized by udpipe

```

```{r eval=FALSE}
saveRDS(mda_processed, "mda_processed.rds")
```

```{r}
mda_processed <- readRDS("mda_processed.rds")
```


```{r}
#Keep those words who appear more than 1% in the document corpus
threshold <- round(1/100 * length(mda_processed$documents),0)

out <- prepDocuments(mda_processed$documents, 
                     mda_processed$vocab,
                     mda_processed$meta,
                     lower.thresh = threshold)
```

```{r eval=FALSE}
saveRDS(out, "out.rds")
```

```{r}
out <- readRDS("out.rds")
```

### 3.1.2 Executing the STM Model
```{r eval=FALSE}
#Finding the optimal number of topics for mda by setting K=0

mda_stm <- stm::stm(documents = out$documents,
                   vocab = out$vocab,
                   K = 0,
                  prevalence =~ price_adj_ratio,
                  max.em.its = 10,
                  data = out$meta,
                  reportevery=10,
                  sigma.prior = 0.7,
                  init.type = "Spectral")
```

```{r eval=FALSE}
saveRDS(mda_stm, "mda_stm_k0.rds")
```

```{r}
mda_stm_k0 <- readRDS("mda_stm_k0.rds")
```


```{r}
# Preview all topics when k=0
summary(mda_stm_k0)
```

```{r eval=FALSE}
#Finding the optimal number of topics
num_topics <- stm::searchK(out$documents,out$vocab,
                     K=c(15, 25, 30, 35, 40),
                     prevalence=~price_adj_ratio, 
                     data=out$meta)
```

```{r eval=FALSE}
saveRDS(num_topics, "num_topics.rds")
```

```{r}
num_topics <- readRDS("num_topics.rds")
```


```{r}
#Plot the stm object to view the percentage of topics in the corpus for k=0
plot(num_topics)

```

The likelihood is the highest at 35 and residual is lowest at 35. Hence, our ideal number of topics would be 35 topics.


```{r}
# Analysing exclusivity vs semantic coherence 
num_topics$results %>%
  select(K, exclus, semcoh) %>%
  filter(K %in% c(15, 20, 25, 30, 35)) %>%
  unnest() %>%
  mutate(K = as.factor(K)) %>%
  ggplot(aes(semcoh, exclus, color = K)) +
  geom_point(size = 2, alpha = 0.7) +
  labs(x = "Semantic Coherence",
       y = "Exclusivity",
       title = "Comparing exclusivity and semantic coherence",
       subtitle = "K = 30 has both high exclusivity and semantic coherence")
```
Looking at semantic coherence and exclusivity, it would seem that the best topic is 35 as marked by the purple dot as it is relatively high for exclusivity and semantic coherence.


### 3.1.3 Displaying words associated with topics in STM

```{r eval=FALSE}
# Now that we have the number of ideal topics, let's execute the model
# Executing the Model when K=35
mda_stm_35 <- stm(documents = out$documents,
                   vocab = out$vocab,
                   K = 35,
                  prevalence =~ price_adj_ratio,
                  max.em.its = 40,
                  data = out$meta,
                  reportevery=3,
                  sigma.prior = 0.7,
                  init.type = "Spectral")
```

```{r eval=FALSE}
saveRDS(mda_stm_35, "mda_stm_35.rds")
```

```{r}
mda_stm_35 <- readRDS("mda_stm_35.rds")
```

```{r}
plot(mda_stm_35)
```

```{r}
library(reshape)
library(tm)
library(wordcloud)


cloud(mda_stm_35,topic = 1)
cloud(mda_stm_35,topic = 2)
cloud(mda_stm_35,topic = 3)
cloud(mda_stm_35,topic = 4)
cloud(mda_stm_35,topic = 5)
cloud(mda_stm_35,topic = 6)
cloud(mda_stm_35,topic = 7)
cloud(mda_stm_35,topic = 8)
cloud(mda_stm_35,topic = 9)
cloud(mda_stm_35,topic = 10)
cloud(mda_stm_35,topic = 11)
cloud(mda_stm_35,topic = 12)
cloud(mda_stm_35,topic = 13)
cloud(mda_stm_35,topic = 14)
cloud(mda_stm_35,topic = 15)
cloud(mda_stm_35,topic = 16)
cloud(mda_stm_35,topic = 17)
cloud(mda_stm_35,topic = 18)
cloud(mda_stm_35,topic = 19)
cloud(mda_stm_35,topic = 20)
cloud(mda_stm_35,topic = 21)
cloud(mda_stm_35,topic = 22)
cloud(mda_stm_35,topic = 23)
cloud(mda_stm_35,topic = 24)
cloud(mda_stm_35,topic = 25)
cloud(mda_stm_35,topic = 26)
cloud(mda_stm_35,topic = 27)
cloud(mda_stm_35,topic = 28)
cloud(mda_stm_35,topic = 29)
cloud(mda_stm_35,topic = 30)
cloud(mda_stm_35,topic = 31)
cloud(mda_stm_35,topic = 32)
cloud(mda_stm_35,topic = 33)
cloud(mda_stm_35,topic = 34)
cloud(mda_stm_35,topic = 35)
```




```{r eval=FALSE}
# We found similarity in some topics and after analysing, noted it can further summarise into 10 topics
# Executing the Model when K=10
mda_stm_10 <- stm(documents = out$documents,
                   vocab = out$vocab,
                   K = 10,
                  prevalence =~ price_adj_ratio,
                  max.em.its = 40,
                  data = out$meta,
                  reportevery=3,
                  sigma.prior = 0.7,
                  init.type = "Spectral")
```

```{r eval=FALSE}
saveRDS(mda_stm_10, "mda_stm_10.rds")
```

```{r}
mda_stm_10 <- readRDS("mda_stm_10.rds")
```


```{r}
cloud(mda_stm_10,topic = 1)
cloud(mda_stm_10,topic = 2)
cloud(mda_stm_10,topic = 3)
cloud(mda_stm_10,topic = 4)
cloud(mda_stm_10,topic = 5)
cloud(mda_stm_10,topic = 6)
cloud(mda_stm_10,topic = 7)
cloud(mda_stm_10,topic = 8)
cloud(mda_stm_10,topic = 9)
cloud(mda_stm_10,topic = 10)
```


### 3.1.4 Plotting relationship between metadata and topics using estimateEffect() in STM

```{r}
#Extracting theta matrix from the fitted object
convergence_theta_mda <- as.data.frame(mda_stm_10$theta)

colnames(convergence_theta_mda) <- paste0("topic_",1:10)

```


```{r}
#Estimate regression using an STM object to incorporate measurement uncertainty from the STM model using the method of composition.
price_adj_ratio_effect <- stm::estimateEffect(~as.numeric(price_adj_ratio),
                                      stmobj = mda_stm_10,
                                      metadata = out$meta,
                                      uncertainty = c("None"))

topic_proportion <- colMeans(mda_stm_10$theta)

#label the topics
topic_labels_stm <- c("Business settlement",
                  "Financial statement",
                  "Revenue management",
                  "Business investment",
                  "Business expansion",
                  "Reneue growth",
                  "Forecast",
                  "Equity management",
                  "Fiscal management",
                  "Liability management")
```


```{r}
# Plot the effects for score rating
plot(price_adj_ratio_effect, covariate = "price_adj_ratio",
     topics = c(1,2,3,4,5,6,7,8,9,10),
     model = mda_stm_10, method = "difference",
     cov.value1 = "100", cov.value2 = "0",
     #xlim = c(-0.010, 0.008),
     xlab = "Low Price Adj Ratio ... High Price Adj Ratio",
     main = "Marginal Effects on Stock Price Adjustment Ratio",
     ci.level = 0.05,
     custom.labels =topic_labels_stm,
     labeltype = "custom")

# Plot the summary effects for price
plot(price_adj_ratio_effect, covariate = "price_adj_ratio",
     topics = c(1:10),
     model = mda_stm_10, method = "continuous",
     cov.value1 = margin2, cov.value2 = margin1,
     xlab = "Low Price Adj Ratio ... High Price Adj Ratio",
     main = "Marginal Change on Topic Probabilities for Low and High Price Adjustment Ratio",
     custom.labels =topic_labels_stm,
     ci.level = 0.05,
     labeltype = "custom")

```

```{r}
## Extracting the theta matrix
convergence_theta <- as.data.frame(mda_stm_10$theta)
colnames(convergence_theta)<-paste0("topic_", 1:10)

#assigning topic summary, proportions and labels to variables
topic_summary <- summary(mda_stm_10)
topic_proportions <- colMeans(mda_stm_10$theta)
topic_labels <- paste0("topic_",1:10)

#wordcloud for topics
stm::cloud(mda_stm_10)

td_beta <- tidy(mda_stm_10)

td_beta

# Calculate stm result for top 20 terms
top_terms <- 
  td_beta %>%
  group_by(topic) %>%
  slice_max(beta, n = 20) %>%
  ungroup() %>%
  arrange(topic, desc(beta))

# Plot stm result for top 20 terms
plot <- top_terms %>%
  mutate(term= reorder(term, beta), topic = factor(topic, labels = topic_labels_stm)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 6, scales = "free") +
  labs (x="Terms", y="Beta", title="Top 20 Terms per Topic Modelling in STM")
  scale_y_reordered()

plot
```

```{r}
library(ggthemes)
library(scales)
library(purrr)

td_gamma <- tidy(mda_stm_10, 
               matrix = "gamma",
               document_names = rownames(out$documents))
td_gamma

gamma_terms <- td_gamma %>%
  group_by(topic) %>%
  summarise(gamma = mean(gamma)) %>%
  arrange(desc(gamma)) %>%
  left_join(top_terms, by = "topic") %>%
  mutate(topic = paste0("Topic ", topic),
         topic = reorder(topic, gamma))

gamma_terms %>%
  select(topic, gamma, term) %>%
  knitr::kable(digits = 3, 
        col.names = c("Topic", "Expected topic proportion", "Top 10 terms"))

# Tidying it up
gamma_topics <- td_gamma %>%
pivot_wider(names_from = topic, values_from = gamma)

# Adding column name
colnames(gamma_topics) <- c("document",topic_labels)

#remove the document from the column
gamma_topics <- as.data.frame(gamma_topics)
rownames(gamma_topics) <- gamma_topics$document
gamma_topics$document <- NULL

#perform PCA
pcav <- FactoMineR::PCA(gamma_topics, graph = FALSE)
factoextra::fviz_pca_var(pcav, alpha.var = .5)
factoextra::fviz_screeplot(pcav, addlabels = TRUE) + theme_classic()
```
The variance explained is shown as high which is a good indication that we have the relevant number of topics.



## 3.2 Latent Dirichlet Allocation (LDA)

### 3.2.1 Processing text data in LDA

```{r}
# Filtering to retain only verbs, nouns and adjectives
mda_filtered <- clean_mda_price%>% filter(upos %in% c("VERB", "NOUN", "ADJ"))
mda_filtered <- mda_filtered %>% select(Accession_Number, price_adj_ratio, return_adj_price, lemma, price_adj_ratio)

# Casting dtm grouping the words by review id
mda_dtm <- mda_filtered %>% count(Accession_Number, lemma) %>% cast_dtm(Accession_Number, lemma,n)

mda_sel_idx <- slam::row_sums(mda_dtm) > 0
mda_dtm <- mda_dtm[mda_sel_idx, ]
```

### 3.2.2 Executing the LDA Model

```{r}
# Computing LDA model to obtain the details of the model fit outlining how words are associated to topics and how topics are associated to documents.
LDA_mda <- topicmodels::LDA(mda_dtm, k=10, method="Gibbs", control = list(seed= 1234))

# Obtaining the per-word-per-topic probability, where the model computes the probability of a specific term being generated from a specific topic.
topics_mda <- tidy(LDA_mda,matrix="beta")
```

```{r eval=FALSE}
saveRDS(topics_mda, "topics_mda_lda.rds")
```

```{r}
topics_mda_lda <- readRDS("topics_mda_lda.rds")
```

### 3.2.3 Displaying words associated with topics in LDA

```{r}
#obtaining the 10 most common terms per topic
top_terms_mda <- topics_mda_lda %>% group_by(topic) %>% top_n(20, beta) %>% ungroup() %>% arrange(topic, -beta)

topic_labels_mda <- c("Business investment",
                  "Financial statement",
                  "Revenue management",
                  "Business settlement",
                  "Fiscal management",
                  "Business operation",
                  "Forecast",
                  "Revenue growth",
                  "Business expansion",
                  "Liability management")

top_terms_mda %>% mutate(term= reorder(term, beta), topic = factor(topic, labels = topic_labels_mda)) %>% ggplot(aes(term, beta, fill=topic))+ geom_col()+ facet_wrap(~topic, scales="free")+ coord_flip() + labs(fill="Topic", y= "Term", x = "Beta") 

```


## 3.3 Additive predictability

Using regression model to estimate additive predictability of management's discussion and analysis topics on price adjustment ratio.

```{r}
#Creating a simple regression table using the lm() functions.
mda_to_regress_topic <- cbind(out$meta, convergence_theta_mda)

mda_model_topic_price <- lm(price_adj_ratio~ topic_1+topic_2+topic_3+topic_4+topic_5+topic_6+topic_7,
                         data = mda_to_regress_topic)
```

### 3.3.1 Corpus level summaries using stargazer on management discussions & analysis

```{r}
#Run stargazer and carry out labelling adjustment
stargazer::stargazer(mda_model_topic_price,
          title="Regression Results",
          align=TRUE,
          type="text",
          covariate.labels = c("Business investment",
                  "Financial statement",
                  "Revenue management",
                  "Business settlement",
                  "Fiscal management",
                  "Business operation",
                  "Forecast",
                  "Revenue growth",
                  "Business expansion",
                  "Liability management"),
          omit.stat=c("LL","ser","f"))
```
### 3.3.2 Corpus level summaries using topicCorr on management discussions & analysis

```{r}
topicCorr_review <- plot(stm::topicCorr(mda_stm_10), 
                         method=c("simple"), 
                         verbose=TRUE, 
                         vlabels = topic_labels)
```










